An Airdrop That Preserves Recipient Privacy

### 2019-01-18 paper/ecdsa.tex
start cleaning up warmup section

\section{A private airdrop to ECDSA and Schnorr public keys}\label{sec:dsa}

\rsw{this section is, for now, a quick note-stash}

As a warm-up, we present a PAD scheme for ECDSA.
\RSW{generalize to EdDSA and prime-field DSA just here, throughout, or just in a comment at the end?}
%
%\paragraph{Notation}
Let $\HH$ be a cyclic group of prime order $q$, generated by $\gHH$.
\RSW{I don't love $\HH$ and I loathe $\gHH$, but maybe it's helpful to use
    different notation here than in the next section. Or maybe this notation
    is so standard it doesn't matter.}

\rsw{maybe standardize on party names, i.e., `challenger' (or `sender'),
    `signer' (or `receiver'), and `verifier'.}

\paragraph{Algorithm $\text{sendTokens}(\PK)$:} To send tokens to public key $\PK = \gHH^x$, do:
\begin{itemize}
\item generate a random $s \rgets \range{q}$
\item output $(c, s)$ where $c \gets \PK\cdot\gHH^s$
\end{itemize}

>>>>

\section{A private airdrop scheme from ECDSA}\label{sec:dsa}

As a warm-up, we present a PAD for ECDSA.
\unskip\footnote{This scheme extends naturally to Schnorr, EdDSA, etc.}
%
%\paragraph{Notation}
Let $\HH = \langle\gHH\rangle$ be a cyclic group of prime order $q$.
\RSW{I don't love $\HH$ and I loathe $\gHH$, but maybe it's helpful to use
    different notation here than in the next section. Or maybe this notation
    is so standard it doesn't matter.}

\paragraph{Algorithm $\text{sendTokens}(\PK)$:} To send tokens to public key $\PK = \gHH^x$, do:
\begin{itemize}
\item choose $s \rgets \range{q}$
\item output $(c, s)$ where $c \gets \PK\cdot\gHH^s$
\end{itemize}
